My title

### 2024-01-30 outputs/paper/paper.qmd
upload first paper.qmd draft

>>>>

```{r}
knitr::opts_chunk$set(echo = FALSE, results = "hide", message = FALSE, warning = FALSE)
```

```{r}
library("tidyverse")
data <- read.csv("~/usa_birthrate/inputs/data/fig_1.csv")

ggplot(data, aes(x = year, y = brate_all)) + 
    geom_line() +
    theme_minimal() +
    labs(title = "US Birth Rates from 1980 to 2020",
         x = "Year",
         y = "Birth Rate per 1,000 women age 15–44")

```

```{r}
data <- read.csv("~/usa_birthrate/inputs/data/fig_2e.csv")

ggplot(data, aes(x = year)) + 
    geom_line(aes(y = brate_married, color = "Married")) +
    geom_line(aes(y = brate_unmarried, color = "Unmarried")) +
    theme_minimal() +
    labs(title = "US Birth Rates by Marital Status (1980-2020)",
         x = "Year",
         y = "Birth Rate",
         color = "Marital Status")

```

```{r}

data <- read.csv("~/usa_birthrate/inputs/data/fig_5.csv")

ggplot() + 
    geom_line(data = data, aes(x = year, y = brate_lesshs, color = "Less than High School")) +
    geom_line(data = data, aes(x = year, y = brate_hsgrad, color = "High School Graduate")) +
    geom_line(data = data, aes(x = year, y = brate_somecoll, color = "Some College")) +
    geom_line(data = data, aes(x = year, y = brate_colgrad, color = "College Graduate")) +
    theme_minimal() +
    labs(title = "US Birth Rates by Education Level (1992-2019)",
         x = "Year",
         y = "Birth Rate",
         color = "Education Level")

```
```{r}

data <- read.csv("~/usa_birthrate/inputs/data/fig_4.csv")
ggplot() + 
    geom_line(data = data, aes(x = year, y = brate_1519, color = "15-19")) +
    geom_line(data = data, aes(x = year, y = brate_2024, color = "20-24")) +
    geom_line(data = data, aes(x = year, y = brate_2529, color = "25-29")) +
    geom_line(data = data, aes(x = year, y = brate_3034, color = "30-34")) +
    geom_line(data = data, aes(x = year, y = brate_3539, color = "35-39")) +
    geom_line(data = data, aes(x = year, y = brate_4044, color = "40-44")) +
    theme_minimal() +
    labs(title = "US Birth Rates by Age Group (1980-2020)",
         x = "Year",
         y = "Birth Rate",
         color = "Age Group")

```
